From heartbeat to data -- Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-10-29 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.Rmd
bla bla bla.. affiliations und so

authornote: |
 We received funding from QualiFond of University Leipzig. We have no conflicts of interest to disclose. This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022). 

@@

    email: gregor@example.com
    affiliation: Max Planck Institute for Evolutionary Anthropology

@@

    affiliation: University of Greifswald

@@

    organization: Division of Empirical School and Classroom Research, Institute of Educational Sciences

@@

  - code: Max Planck Institute for Evolutionary Anthropology
    organization: Department
    addressline: Deutscher Pl. 6
    postcode: "04103"

@@

  - code: University of Greifswald
    organization: Division of Health and Prevention, Institute of Psychology

@@

\begin{table}[ht]
    \centering
    \begin{tabularx}{\textwidth}{lXXXXXX}
        \toprule
        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
        \midrule
        Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ ($I_1$)\\
        Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ ($I_2$)\\
        Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ ($I_3$)\\
        Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ ($I_4$)\\
        End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 ($I_5$)\\
        \bottomrule
    \end{tabularx}
    \caption{Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
    \label{tab_2}
\end{table}

>>>>

authornote: "|
 We received funding from QualiFond of University Leipzig. We have no conflicts of interest to disclose. This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022)." 

@@

@@

    affiliation: UoG, DZKJ
    email: gregor.kachel@gmail.com

@@

    organization: Leipzig University Division of Empirical School and Classroom Research, Institute of Educational Sciences

@@

  - code: UoG
    organization: University of Greifswald, Division of Health and Prevention, Institute of Psychology

@@

  - code: DZKJ
    organization: German Center for Child and Adolescent Health (DZKJ)

@@

\begin{table}[ht]
    \centering
    \begin{tabularx}{\textwidth}{lXXXXXX}
        \toprule
        Interval  & \multicolumn{2}{c}{\textit{M} (\textit{SD})} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
        \midrule
        Pre-teaching interval (I$_1$) & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
        Teaching interval (I$_2$) & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
        Post-teaching interval (I$_3$) & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
        Interview interval (I$_4$) & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
        End interval (I$_5$) & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
        \bottomrule
    \end{tabularx}
    \caption{Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
    \label{tab_2}
\end{table}

### 2024-10-29 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.tex
bla bla bla.. affiliations und so

  \title{From heartbeat to data -- Using wearable fitness trackers as an
affordable approach to assess teacher stress}
    \author[Leipzig University]{Mandy Klatt%
  \corref{cor1}%
  \fnref{1}}
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[Leipzig University]{Christin Lotz%
  %
  \fnref{2}}
   \ead{christin.lotz@uni-leipzig.de} 
    \author[Max Planck Institute for Evolutionary Anthropology]{Gregor
Kachel%
  %
  \fnref{3}}
   \ead{gregor@example.com} 
    \author[University of Greifswald]{Peer Keßler%
  %
  \fnref{4}}
   \ead{peer.kessler@uni-greifswald.de} 
    \author[Leipzig University]{Anne Deiglmayr%
  %
  \fnref{5}}
   \ead{anne.deiglmayr@uni-leipzig.de} 
      \affiliation[Leipzig University]{
    organization={Division of Empirical School and Classroom Research,
Institute of Educational Sciences},addressline={Marschnerstr.
29},city={Leipzig},postcode={04109},country={Germany},}
    \affiliation[Max Planck Institute for Evolutionary Anthropology]{
    organization={Department},addressline={Deutscher Pl.
6},city={Leipzig},postcode={04103},country={Germany},}
    \affiliation[University of Greifswald]{
    organization={Division of Health and Prevention, Institute of
Psychology},addressline={Robert-Blum-Str.
13},city={Greifswald},postcode={17489},country={Germany},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{Conceptualization, Methodology, Formal analysis,
Investigation, Data Curation, Writing - Original Draft}
    \fntext[2]{Conceptualization, Methodology, Writing - Review \&
Editing, Supervision}
    \fntext[3]{Formal analysis, Data Curation, Writing - Review \&
Editing}
    \fntext[4]{Conceptualization, Methodology, Writing - Review \&
Editing}
    \fntext[5]{Conzeptualization, Methodology, Writing - Review \&
Editing, Supervision}

>>>>

  \title{From heartbeat to data -- Using wearable fitness trackers as an
affordable approach to assess teacher stress}
    \author[Leipzig University]{Mandy Klatt%
  \corref{cor1}%
  \fnref{1}}
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[Leipzig University]{Christin Lotz%
  %
  \fnref{2}}
   \ead{christin.lotz@uni-leipzig.de} 
    \author[UoG, DZKJ]{Peer Keßler%
  %
  \fnref{3}}
   \ead{peer.kessler@uni-greifswald.de} 
    \author[Leipzig University]{Gregor Kachel%
  %
  \fnref{4}}
   \ead{gregor.kachel@gmail.com} 
    \author[Leipzig University]{Anne Deiglmayr%
  %
  \fnref{5}}
   \ead{anne.deiglmayr@uni-leipzig.de} 
      \affiliation[Leipzig University]{
    organization={Leipzig University Division of Empirical School and
Classroom Research, Institute of Educational
Sciences},addressline={Marschnerstr.
29},city={Leipzig},postcode={04109},country={Germany},}
    \affiliation[UoG]{
    organization={University of Greifswald, Division of Health and
Prevention, Institute of Psychology},addressline={Robert-Blum-Str.
13},city={Greifswald},postcode={17489},country={Germany},}
    \affiliation[DZKJ]{
    organization={German Center for Child and Adolescent Health
(DZKJ)},addressline={Robert-Blum-Str.
13},city={Greifswald},postcode={17489},country={Germany},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{Conceptualization, Methodology, Formal analysis,
Investigation, Data Curation, Writing - Original Draft}
    \fntext[2]{Conceptualization, Methodology, Writing - Review \&
Editing, Supervision}
    \fntext[3]{Conceptualization, Methodology, Writing - Review \&
Editing}
    \fntext[4]{Formal analysis, Data Curation, Writing - Review \&
Editing}
    \fntext[5]{Conzeptualization, Methodology, Writing - Review \&
Editing, Supervision}
